\Large\textbf{PixelBytes: Catching Unified Embedding for Multimodal Generation}

### 2024-09-01 docs/paper/article.tex
train an optimal model for generation - Stride 1 and 1000 Epoch

\subsection{Model Architectures}
We tested three different model types: Recurrent Neural Network (RNN) using bidirectional Long Short-Term Memory (LSTM) units \cite{hochreiter1997long}, Transformer \cite{vaswani2017attention}, and Mamba, which is based on the State Space Model (SSM) \cite{gu2022efficiently}. Each model was adapted to work with our dataset of pixel data and bytecode sequences. We trained the models on Kaggle using dual T4 GPUs. We used a batch size of 32, sequence length of 256, learning rate of 0.001, and trained for 200 epochs, checking the model's performance every 5 epochs. The trained models are available at \url{https://huggingface.co/ffurfaro/PixelBytes-Pokemon}.

@@

In contrast, the LSTMs (referred to as RNNs in our analysis) demonstrated more balanced performance. The closer alignment of their training and validation curves indicates they may generalize better to unseen data. The Transformer model had the lowest performance among the three. This could be due to the absence of positional encoding, which is important for Transformers in sequence tasks.

>>>>

\subsection{Model Architectures}
We evaluated three compact model architectures, each with fewer than 100,000 parameters: a Recurrent Neural Network (RNN) using bidirectional Long Short-Term Memory (LSTM) units \cite{hochreiter1997long}, a Transformer \cite{vaswani2017attention}, and Mamba, based on the State Space Model (SSM) \cite{gu2022efficiently}. These models were adapted to process our dataset of pixel data and bytecode sequences. Training was conducted on Kaggle using dual T4 GPUs, with a batch size of 32, sequence length of 256, stride size of 32, and learning rate of 0.001. We trained for 200 epochs, evaluating performance every 5 epochs. The resulting models are available at \url{https://huggingface.co/ffurfaro/PixelBytes-Pokemon}. Additionally, we developed a more specialized model for generation tasks, which is not presented in this paper.

@@

In contrast, the LSTMs (referred to as RNNs in our analysis) demonstrated more balanced performance. The closer alignment of their training and validation curves indicates they may generalize better to unseen data. The Transformer model had the lowest performance among the three. This could be due to the absence of positional encoding trick, which is important for Transformers in sequence tasks.
